Fig3

### 2020-05-23 analysis/03_datawrangling.Rmd
better fig1 and suppl fig 1
fig 3 from thursday

# note: I can't find these genes in dataset: NOS1 or OXTR or FOX1B or HTR5A
```

@@

allvsd <- vsd_pathfiles %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x), .id = "file_name")  %>% 
  dplyr::rename("gene" = "X1") %>% 
  pivot_longer(cols = L.G118_female_gonad_control:y98.o50.x_male_pituitary_inc.d3, 
               names_to = "samples", values_to = "counts") 
allvsd %>% select(-file_name) %>% head()
```

>>>>

# note: I can't find these genes in dataset: NOS1 or OXTR or FOX1B or HTR5A

GOgeneonly <- parentalcaregenes %>%
  filter(GO != "") %>%
  pull(GO)
GOgeneonly
```

@@

allvsd <- vsd_pathfiles %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x), .id = "file_name")  %>% 
  dplyr::rename("gene" = "X1") %>% 
  pivot_longer(cols = L.G118_female_gonad_control:y98.o50.x_male_pituitary_inc.d3, 
               names_to = "samples", values_to = "counts") 
allvsd %>% select(-file_name) %>% head()

### 2020-05-23 analysis/06_datawrangling.Rmd
now working for fig 3... but includes manip data...
fig 3 from thursday

---
title: "05_wrangle"
output: md_document
---

@@

head(allvsd)
```

@@

```{r}

@@

```{R}
write.csv(candidatevsd, "../results/06_candidatevsd.csv", row.names = F)
write.csv(allDEG, "../results/06_allDEG.csv", row.names = F)
```

>>>>

---
title: "06_wrangle"
output: md_document
---

@@

head(allvsd)

library(stringr)
allvsd %>%
  filter(str_detect(samples, "Merc"))

@@

```{r genelists}

@@

```{R}
write.csv(candidatevsd, "../results/06_candidatevsd.csv", row.names = F)
write.csv(allDEG, "../results/06_allDEG.csv", row.names = F)

candidategenes
```

### 2020-05-23 analysis/figure-3.Rmd
now with box plots
fig 3 from thursday

```{r savefiles}
write.csv(PRLpit,"../results/PRLvsd.csv", row.names = F)

>>>>

```{r savefiles}
write.csv(PRLpit,"../results/PRLvsd.csv", row.names = F)
```

## PRL and PRLR in three tissues

```{r}
p1 <- candidateboxplot("hypothalamus", c("PRL"), sexlevels) + labs(subtitle = "hypothalamus", title = "PRL")
p2 <- candidateboxplot("pituitary", c("PRL"), sexlevels) + labs(subtitle = "pituitary")
p3 <- candidateboxplot("gonad", c("PRL"), sexlevels) + labs(subtitle = "gonads") + theme(axis.text.x = element_text(angle = 45))

p4 <- candidateboxplot("hypothalamus", c("PRLR"), sexlevels) + labs(subtitle = "blood", title = " ") 
p5 <- candidateboxplot("pituitary", c("PRLR"), sexlevels) + labs(subtitle = "cropmilk")
p6 <- candidateboxplot("gonad", c("PRLR"), sexlevels) + theme(axis.text.x = element_text(angle = 45))+ labs(subtitle = "spleen")

plot_grid(p1,p4,p2,p5,p3,p6, ncol = 2, rel_heights = c(1.2,1,1.2))
